Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma

### 2017-06-19 main.tex
Add payoff plots
Add winplots

\begin{landscape}
    \includegraphics[width=\paperwidth]{plots/Standard_boxplot.pdf}
\end{landscape}

% \includegraphics{strategies_std_boxplot.svg}
% \includegraphics{strategies_std_payoff.svg}
% \includegraphics{strategies_std_winplot.svg}

@@

\begin{landscape}
    \includegraphics[width=\paperwidth]{plots/Noisy_boxplot.pdf}
\end{landscape}
% \includegraphics{strategies_noisy_payoff.svg}
% \includegraphics{strategies_noisy_winplot.svg}

>>>>

\begin{landscape}
    \begin{figure}[!hbtp]
        \includegraphics[width=\paperwidth]{plots/Standard_boxplot.pdf}
        \caption{Ranking by Median Payoff for the Standard Tournament}
    \end{figure}
\end{landscape}

\begin{landscape}
    \begin{figure}[!hbtp]
        \includegraphics[width=\paperwidth]{plots/Standard_winplot.pdf}
        \caption{Ranking by Total wins for the Standard Tournament}
    \end{figure}
\end{landscape}

\begin{figure}[!hbtp]
    \includegraphics[width=\paperwidth]{plots/Standard_payoff.pdf}
    \caption{Pairwise Match results for the Standard Tournament}
\end{figure}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \includegraphics[width=\paperwidth]{plots/Noisy_boxplot.pdf}
        \caption{Ranking by Median Payoff for the Noisy Tournament}
    \end{figure}
\end{landscape}

\begin{landscape}
    \begin{figure}[!hbtp]
        \includegraphics[width=\paperwidth]{plots/Noisy_winplot.pdf}
        \caption{Ranking by Total wins for the Noisy Tournament}
    \end{figure}
\end{landscape}

\begin{figure}[!hbtp]
    \includegraphics[width=\paperwidth]{plots/Noisy_payoff.pdf}
    \caption{Pairwise Match results for the Noisy Tournament}
\end{figure}
